\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-10-20 fully-abstract-comp/popl2019/paper.tex
Propose some re-inlinings in Fig.10, 11, 12.
Further minor refactoring in getCallSeal.
Reduce the crammedness of Fig. 10 with some latex relayouting...
Further Figure 10 refactoring
- Changed the order of sealReturnPair arguments to be the same order as result.
- Changed c_priv_stk to c_local in aux definition for consistency.
- Formatting
Removed sealedPairArgument aux definition
It looks like this definition had become obsolete.
Reorder aux definitions to match the order in definitions
Put scall on one line

  \begin{tabular}{|>{$}c<{$}|p{3.7cm}|>{\raggedright\arraybackslash}p{6.55cm}|}

@@

    \scall{\srcalt{\offpc,\offsigma}}{\src{r_1}}{\src{r_2}} &

@@

    $\sigma = \var{getCallSeal}(\Phi.\reg,\Phi.\mem,\offpc,\offsigma)$ and 
    $s_c,s_d = \var{sealReturnPair}(\sigma,c_\var{local},c_\opc)$ and

@@

      \src{\var{retPtrMatchesOpc}(c_1,\opc)}\\
      \src{\var{retPtrForLocalStack}(c_2,\ms_\var{local})}\\
      \src{c_\stk = \var{reconstructStackPointer}(\reg,c_2) \tand}\\
      \src{c_\opc =  \var{tokenToPc}(c_1)} 

@@

\begin{figure}
    \[
      \src{\var{sealedPairArgument}(\reg,r_1,r_2,c_1,c_2)} \mathit{ iff }
      \left\{ 
      \begin{array}{l}
        \src{\exists \sigma \ldotp (\reg(r_1) = \sealed{\sigma, c_1} \wedge \reg(r_2) = \sealed{\sigma, c_2}) \wedge{}}\\
        \src{r_1 \neq \rtmp{1} \wedge r_2 \neq \rtmp{2}}
      \end{array}
      \right.
    \]
    \[
      \src{ \opc, c_\opc = \var{setupOpc(((\_,\_),\baddr,\eaddr,\aaddr))}} \mathit{ iff }
      \left\{ 
      \begin{array}{l}
      \src{\opc = \aaddr + \calllen \wedge{}}\\
      \src{c_\opc = \retptrc(\baddr,\eaddr,\opc) \wedge{}}
      \end{array}
       \right.
    \]
    \begin{multline*}
      \src{\ms_{\stk,\var{local}},c_\var{local\_data},\ms_{\stk,\var{unused}},c_\stk = \var{splitStack}(\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk}, \ms_\stk)} \mathit{\ iff} \\
      \left\{ 
      \begin{array}{l}
      \src{\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk }\\
      \src{\ms_{\stk,\var{local}} = \ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42} }\\
      \src{\ms_{\stk,\var{unused}} = \ms_\stk|_{[\baddr_\stk,\aaddr_\stk-1]} }\\
      \src{c_\stk = \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1} }\\
      \src{c_\var{local\_data} = \retptrd(\aaddr_\stk,\eaddr_\stk) }\\
      \end{array}
      \right.
    \end{multline*}
    \[
      \src{\sigma = \var{getCallSeal}(\reg,\mem,\offpc,\offsigma)} \mathit{\ iff\ }
      \left\{
      \begin{array}{l} 
      \src{\reg(\pcreg) = ((\_,\_),\baddr,\eaddr,\aaddr) \wedge \baddr \leq  \aaddr+\offpc \leq \eaddr \wedge{}} \\
      \src{\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr} \wedge{} \sigma_\baddr \leq \sigma \leq \sigma_\eaddr \wedge{}}\\
      \src{\sigma = \sigma_\aaddr + \offsigma }
      \end{array}
      \right.
    \]

    \[
     \src{s_c,s_d = \var{sealReturnPair}(\sigma,c_\var{priv\_data},c_\opc)} \mathit{\ iff\ }
      \src{s_d = \sealed{\sigma,c_\var{priv\_data}} \wedge{} s_c = \sealed{\sigma,c_\opc}}
    \]
  % \begin{multline*}
  %   \src{\var{callConditions}(r_1,r_2,\offpc,\offsigma,(\mem,\reg,\stk,\ms_\stk)) = (\mem,\reg',\stk',\ms_{\stk,\var{rest}})}\mathit{\ iff}\\
  %     \quad\quad\left\{ 
  %       \begin{array}{l}
  %         \src{\var{sealedPairArgument}(\reg,r_1,r_2,c_1,c_2)}\\
  %     \src{\ms_{\stk,\var{local}},\ms_{\stk,\var{rest}},c_\stk,c_\var{local\_data} = \var{splitStack}(\reg, \ms_\stk) \wedge{}}\\
  %     \src{\opc, c_\opc =\var{setupOpc(\reg)} \wedge{}}\\
  %     \src{\stk' = (\opc,\ms_{\stk,\var{local}}) :: \stk \wedge{}}\\
  %     \src{\sigma = \var{getCallSeal}(\reg,\mem,\offpc,\offsigma) \wedge{}}\\
  %     \src{s_c,s_d = \var{sealReturnPair}(\sigma,c_\var{local\_data},c_\opc) \wedge{}}\\
  %     \src{w_1,w_2 = \linCons{\reg(r_1),\reg(r_2)} \wedge{}}\\ 
  %     \src{\reg' =\reg\updReg{r_1,r_2}{w_1,w_2}\updReg{\rretc,\rretd}{s_c,s_d}\updReg{\rstk,\rtmp{1}}{c_\stk,0}}
  %     \end{array}\right.
  % \end{multline*}

  \caption{The call condition in the operational semantics of \srccm{}.}
  \label{fig:source-op-sem}
\end{figure}
\begin{figure}
\[
    \src{\stkptr{\rw,\stkb,\eaddr_\stk,\aaddr_\stk} = \var{tokenToStkPtr}(\retptrd(\aaddr_\stk,\eaddr_\stk)}
\]
\[
    \src{((\rx,\normal),\baddr,\eaddr,\opc) = \var{tokenToPc}(\retptrc(\baddr,\eaddr,\opc)}
\]
% \[
%     \src{\stk', \ms_\var{local\_stk} = \var{popCallStackFrame} (\stk,c_1,c_2)}
%     \mathit{\ iff\ }
%       \left\{ \array{l}
%         \src{\stk = (\opc, \ms_\var{local\_stk}) :: \stk' \wedge{}} \\
%         \src{c_1 = \retptrc(\_,\_,\opc) \wedge{}} \\
%         \src{c_2 = \retptrd(\aaddr_\stk,\eaddr_\stk)\wedge{}} \\
%         \src{\dom(\ms_\var{local\_stk}) \subseteq [\aaddr_\stk,\eaddr_\stk]}
%         \endarray
%      \right.
% \]
\[
  \src{\var{retPtrMatchesOpc(\retptrc(\_,\_,\opc_c),\opc)}} \mathit{\ iff\ } \src{\opc_c = \opc}
\]
\[
  \src{\var{retPtrForMatchLocalStack(\retptrd(\aaddr_\stk,\eaddr_\stk),\ms_\var{local})}} \mathit{\ iff\ } \src{\dom(\ms_\var{local} \subseteq [\aaddr_\stk,\eaddr_\stk])}
\]

\[
    \src{c_\stk = \var{reconstructStackPointer}(\reg,c)}
    \mathit{\ iff\ }
      \left\{ \array{l}
        \src{c = \retptrd(\aaddr_\stk,\eaddr_\stk) \wedge{}} \\
        \src{\reg(\rstk) = \stkptr{\rw, \stkb, \aaddr_\stk-1,\_} \wedge{}} \\
        \src{\stkb \leq \addr_\stk \wedge{}} \\
        \src{c_\stk = \var{tokenToStkPtr(c)} }
        \endarray
     \right.
\]

% \begin{multline*}
%     \src{(\mem,\reg',\stk',\ms_\stk') = \var{returnCondition}(c_1,c_2,(\mem,\reg,\stk,\ms_\stk))}\mathit{\ iff\ }\\
%       \quad\quad\left\{ 
%       \begin{array}{l}
%       \src{\stk', \ms_\var{local\_stk} = \var{popCallStackFrame}(\stk,c_1,c_2)}\\
%       \src{c_\stk = \var{reconstructStackPointer}(\reg,c_2)}\\
%       \src{c_\opc =  \var{tokenToPc}(c_1)} \\
%       \src{\ms_\stk' = \ms_\stk \uplus \ms_\var{local\_stk}} \\
%       \src{\reg' =\reg\updReg{\pcreg,\rstk}{c_\opc,c_\stk}\updReg{\rdata,\rtmp{1},\rtmp{2}}{0,0,0}}
%       \end{array}\right.
%   \end{multline*}

  \caption{The return condition in the operational semantics of \srccm{}.}
  \label{fig:source-op-sem-return}

>>>>

  \begin{tabular}{|>{$}c<{$}|p{3.7cm}|>{\raggedright\arraybackslash}p{6.6cm}|}

@@

    \arraycolsep=0pt\array{c}
    \scall{\srcalt{\offpc,\offsigma}}{\src{r_1}}{\src{r_2}}
    \endarray &

@@

    $\sigma =\begin{multlined}[t]
      \var{getCallSeal}(\\
      \Phi.\reg(\pcreg), \Phi.\mem,\offpc,\offsigma)  \text{ and }
    $s_c,s_d = \var{sealReturnPair}(\sigma,c_\opc,c_\var{local})$ and

@@

      \src{c_1 = \retptrc(\baddr,\eaddr,\opc)}\\
      \src{c_2 = \retptrd(\aaddr_\stk,\eaddr_\stk) \wedge \dom(\ms_\var{local}) \subseteq [\aaddr_\stk,\eaddr_\stk]}\\
      \src{c_\stk = \var{reconstructStackPointer}(\reg(\rstk),c_2) \tand}\\
      \src{c_\opc =  ((\rx,\normal),\baddr,\eaddr,\opc)} 

@@

\begin{figure}
    \begin{multline*}
      \src{\ms_{\stk,\var{local}},c_\var{local\_data},\ms_{\stk,\var{unused}},c_\stk = \var{splitStack}(\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk}, \ms_\stk)} \mathit{\ iff\ } \\
      \left\{ 
      \begin{array}{l}
      \src{\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk }\\
      \src{\ms_{\stk,\var{local}} = \ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42} }\\
      \src{\ms_{\stk,\var{unused}} = \ms_\stk|_{[\baddr_\stk,\aaddr_\stk-1]} }\\
      \src{c_\stk = \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1} }\\
      \src{c_\var{local\_data} = \retptrd(\aaddr_\stk,\eaddr_\stk) }\\
      \end{array}
      \right.
    \end{multline*}
    \[
      \src{ \opc, c_\opc = \var{setupOpc(((\_,\_),\baddr,\eaddr,\aaddr))}} \mathit{\ iff\ }
      \left\{ 
      \begin{array}{l}
      \src{\opc = \aaddr + \calllen \wedge{}}\\
      \src{c_\opc = \retptrc(\baddr,\eaddr,\opc) \wedge{}}
      \end{array}
       \right.
    \]
    \[
      \src{\sigma = \var{getCallSeal}(c_\pcreg,\mem,\offpc,\offsigma)} \mathit{\ iff\ }
      \left\{
      \begin{array}{l} 
      \src{c_\pcreg = ((\_,\_),\baddr,\eaddr,\aaddr) \wedge \baddr \leq  \aaddr+\offpc \leq \eaddr \wedge{}} \\
      \src{\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr} \wedge{} \sigma_\baddr \leq \sigma \leq \sigma_\eaddr \wedge{}}\\
      \src{\sigma = \sigma_\aaddr + \offsigma }
      \end{array}
      \right.
    \]

    \[
     \src{\sealed{\sigma,c_\opc},\sealed{\sigma,c_\var{local}} = \var{sealReturnPair}(\sigma,c_\opc,c_\var{local})}
    \]
  % \begin{multline*}
  %   \src{\var{callConditions}(r_1,r_2,\offpc,\offsigma,(\mem,\reg,\stk,\ms_\stk)) = (\mem,\reg',\stk',\ms_{\stk,\var{rest}})}\mathit{\ iff}\\
  %     \quad\quad\left\{ 
  %       \begin{array}{l}
  %         \src{\var{sealedPairArgument}(\reg,r_1,r_2,c_1,c_2)}\\
  %     \src{\ms_{\stk,\var{local}},\ms_{\stk,\var{rest}},c_\stk,c_\var{local\_data} = \var{splitStack}(\reg, \ms_\stk) \wedge{}}\\
  %     \src{\opc, c_\opc =\var{setupOpc(\reg)} \wedge{}}\\
  %     \src{\stk' = (\opc,\ms_{\stk,\var{local}}) :: \stk \wedge{}}\\
  %     \src{\sigma = \var{getCallSeal}(\reg,\mem,\offpc,\offsigma) \wedge{}}\\
  %     \src{s_c,s_d = \var{sealReturnPair}(\sigma,c_\var{local\_data},c_\opc) \wedge{}}\\
  %     \src{w_1,w_2 = \linCons{\reg(r_1),\reg(r_2)} \wedge{}}\\ 
  %     \src{\reg' =\reg\updReg{r_1,r_2}{w_1,w_2}\updReg{\rretc,\rretd}{s_c,s_d}\updReg{\rstk,\rtmp{1}}{c_\stk,0}}
  %     \end{array}\right.
  % \end{multline*}

  \begin{multline*}
    \src{\var{reconstructStackPointer}(\stkptr{\rw, \stkb, \aaddr_\stk-1,\_},\retptrd(\aaddr_\stk,\eaddr_\stk)) =}\\ \src{\stkptr{\rw,\stkb,\eaddr_\stk,\aaddr_\stk}} \mathit{\ iff\ }
        \src{\stkb \leq \addr_\stk }
   \end{multline*}

  \caption{Auxiliary definitions used in the operational semantics of \srccm{}.}
  \label{fig:source-op-sem}
\end{figure}
% \begin{figure}
% % \[
% %     \src{\stkptr{\rw,\stkb,\eaddr_\stk,\aaddr_\stk} = \var{tokenToStkPtr}(\retptrd(\aaddr_\stk,\eaddr_\stk)}
% % \]
% % \[
% %     \src{\stk', \ms_\var{local\_stk} = \var{popCallStackFrame} (\stk,c_1,c_2)}
% %     \mathit{\ iff\ }
% %       \left\{ \array{l}
% %         \src{\stk = (\opc, \ms_\var{local\_stk}) :: \stk' \wedge{}} \\
% %         \src{c_1 = \retptrc(\_,\_,\opc) \wedge{}} \\
% %         \src{c_2 = \retptrd(\aaddr_\stk,\eaddr_\stk)\wedge{}} \\
% %         \src{\dom(\ms_\var{local\_stk}) \subseteq [\aaddr_\stk,\eaddr_\stk]}
% %         \endarray
% %      \right.
% % \]
% % \[
% %   \src{\var{retPtrForMatchLocalStack(\retptrd(\aaddr_\stk,\eaddr_\stk),\ms_\var{local})}} \mathit{\ iff\ } \src{\dom(\ms_\var{local} \subseteq [\aaddr_\stk,\eaddr_\stk])}
% % \]

% % \begin{multline*}
% %     \src{(\mem,\reg',\stk',\ms_\stk') = \var{returnCondition}(c_1,c_2,(\mem,\reg,\stk,\ms_\stk))}\mathit{\ iff\ }\\
% %       \quad\quad\left\{ 
% %       \begin{array}{l}
% %       \src{\stk', \ms_\var{local\_stk} = \var{popCallStackFrame}(\stk,c_1,c_2)}\\
% %       \src{c_\stk = \var{reconstructStackPointer}(\reg,c_2)}\\
% %       \src{c_\opc =  \var{tokenToPc}(c_1)} \\
% %       \src{\ms_\stk' = \ms_\stk \uplus \ms_\var{local\_stk}} \\
% %       \src{\reg' =\reg\updReg{\pcreg,\rstk}{c_\opc,c_\stk}\updReg{\rdata,\rtmp{1},\rtmp{2}}{0,0,0}}
% %       \end{array}\right.
% %   \end{multline*}

%   \caption{The return condition in the operational semantics of \srccm{}.}
%   \label{fig:source-op-sem-return}
